---
title: "COVID-19 hospital admissions forecasts (ECDC hub)"
author:
  - "Sophie Meakin"
date: "`r Sys.Date()`"
output:
  md_document:
    variant: markdown_github
    toc: true
    toc_depth: 1
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(technocolour)
source(here::here("R", "data_fns.R"))
source(here::here("R", "plot_fns.R"))
source(here::here("R", "utils.R"))

```

```{r, include = FALSE}

fdate <- lubridate::floor_date(lubridate::today(),
                               unit = "week",
                               week_start = 6)

raw_dat <- load_data(end_date = fdate)

fcast_ids <- get_forecast_ids(dat = raw_dat,
                              forecast_date = fdate) %>%
  # TEMPORARY: keep only locations with no data lag
  filter(last_rep == max(last_rep))

fcast_countries <- raw_dat %>%
  filter(location %in% fcast_ids$id) %>%
  select(contains("location")) %>%
  unique() %>%
  mutate(location_print = paste0(location_name, " (", location, ")")) %>%
  arrange(location_print)

g_admissions <- plot_forecasts(dat_obs = raw_dat,
                               forecast_date = fdate,
                               regions = fcast_ids$id,
                               models = c(
                                 "Time series ensemble",
                                 "ARIMA regression",
                                 "Case-convolution"
                               ))

```

# COVID-19 hospital admissions forecasts for the ECDC Forecast Hub

## Current forecasts

The most recent forecasts (from `r format.Date(fdate, format = "%d %B %Y")`) cover the following locations: `r paste(fcast_countries$location_print, collapse = ", ")`.

```{r current_forecast, echo = FALSE, fig.height = 9, fig.width = 14, dpi = 300}

g_admissions +
  scale_color_brewer(palette = "Set2") +
  scale_fill_brewer(palette = "Set2")

```

## Methods

### Autoregressive time series ensemble

A mean ensemble of three autoregressive time series models: ARIMA, ETS and a "naive" model (where future admissions are equal to the most-recently observed admissions). Each of the three time series models are fit independently to weekly incident admissions data. The mean-ensemble quantile forecast is made by taking the mean of the three quantile forecasts.

### ARIMA regression

A regression model with ARIMA errors, with 1-week lagged COVID-19 cases as a predictor. The model is fit with weekly admissions/cases data. To make forecasts of future admissions for a forecast horizon of two weeks or more, we use the [ECDC Hub ensemble case forecast](https://github.com/epiforecasts/covid19-forecast-hub-europe/tree/main/data-processed/EuroCOVIDhub-ensemble).

### Case convolution

A convolution of COVID-19 cases and a report-to-admission delay distribution. The model is fit with weekly admissions/cases data. To make forecasts of future admissions, we use the [ECDC Hub ensemble case forecast](https://github.com/epiforecasts/covid19-forecast-hub-europe/tree/main/data-processed/EuroCOVIDhub-ensemble).

